\chapter{Conclusion} \label{cha:conclusion}
    %TODO Focus on the final state of the project.
    %     Include how the project meets the set standards and requirements, 
    %     and elaborate on how it could be improved.
    %
    %     Also reflect on the process as a whole, and indicate bottlenecks 
    %     we encountered during development.
    
    Despite some rocky development, we ended up with a fully playable game in
    week 9 that met all of the must have and almost all of the should have
    requirements. The should have requirements included mirror elevations, but
    we found that this wouldn't work well in practice and replaced this feature
    with portals. Those accomplish the same purpose of transferring a laser beam
    across a wall. We've also done away with color combiners because the results
    of mixing colors would be too complicated for players. The game can support
    this, however, and these color mixers would be easy to implement. The main
    takeaway here is that some of the should haves were not met for gameplay
    reasons rather than technical problems.

    The only component of the game that is still rather lacking is the one that
    gave us the most trouble during development: marker tracking with AR
    glasses. The glasses we are using for the game (Meta One) represent the
    state-of-the-art of augmented reality see-through glasses, but they have a
    field-of-view of just 35 degrees and a marker tracking framerate of about 5.
    The first issue causes players to have a lack of overview unless they take
    quite a few steps back from the table. The second issue causes the mirrors
    to lag behind when the player moves their view, which diminishes the
    immersion of the game. We repeatedly contacted the company behind the
    eyewear, but there were no plans to improve on these issues any time soon.

    Despite these limitations of the augmented reality technology, we have been
    able to produce a fun and complete game to play that can be used to
    experiment with situational awareness like the client desired.